### 2017-04-09 paper/oopsla17-submission/evaluation-accuracy.tex
misc

\paragraph{Our Classifiers}
We evaluate five classifiers, each trained on the full set of features.
% features: 44 local syntactic features, 176 contextual syntactic
% features, 55 typing features, and a single expression size feature.
% %
% \ES{should explain the make-up of these groups}
%
% We preemptively discard expressions that are not part of the minimal
% type error slice --- we will explain the rationale for this in
% \autoref{sec:feature-utility} --- and thus the final feature count is
% 276.
%
Our classifiers are:
%
\begin{description}
\item[\linear] A logistic regression trained with a learning rate
  $\eta = 0.001$, an $L_2$ regularization rate $\lambda = 0.001$, and a
  mini-batch size of 200.
\item[\dectree] A decision tree trained with the \ES{HUMA?} algorithm and \ES{HUMA: hyperparams?}.
\item[\forest] A random forest trained with the \ES{HUMA?} algorithm and 30 estimators \ES{HUMA: hyperparams?}.
\item[\hiddenT and \hiddenFH] Two multi-layer perceptron neural networks, both trained with $\eta = 0.001$,
  $\lambda = 0.001$, and a mini-batch size of 200. The first MLP
  contains a single hidden layer of 10 neurons, and the second contains
  a hidden layer of 500 neurons. This allows us to investigate how well
  the MLP can \emph{compress} its model (cf.~\cite{FIXME}). The neurons
  use rectified linear units (ReLU) as their activation function, a
  common practice in modern neural networks.
\end{description}
%
All classifiers were trained for 20 epochs on one dataset
--- \ie they were shown each program 20 times ---
before being evaluated on the other.
%
The logistic regression and MLPs were trained with the \textsc{Adam}
optimizer \citep{Kingma2014-ng}, a variant of stochastic gradient
descent that has been found to converge faster.

@@

\paragraph{Results}
\autoref{fig:accuracy-results} shows the results of our experiment.
%
Localizing the type errors in our benchmarks amounted, on average, to
selecting one of 3 correct locations out of a slice of 10.
%
Our baseline of selecting at random achieves 30\% Top-1
accuracy (58\% Top-3), while \ocaml achieves a Top-1 accuracy of 45\%.
%
Interestingly, one only needs two \emph{random} guesses to outperform
\ocaml, with 47\% accuracy.
%
\sherrloc outperforms both baselines with 56\% Top-1 accuracy (84\% Top
3), while \mycroft actually underperforms \ocaml with 38--41\% Top-1
accuracy.
%
Finally, we find that \emph{all} of our classifiers outperform \sherrloc,
ranging from 59--63\% Top-1 accuracy (86--88\% Top-3) for the \linear
classifier to 70--74\% Top-1 accuracy (91--92\% Top-3) for the \hiddenFH.

>>>>

\paragraph{Our Classifiers}
We evaluate five classifiers, each trained on the full set of features.
% features: 44 local syntactic features, 176 contextual syntactic
% features, 55 typing features, and a single expression size feature.
% %
% \ES{should explain the make-up of these groups}
%
% We preemptively discard expressions that are not part of the minimal
% type error slice --- we will explain the rationale for this in
% \autoref{sec:feature-utility} --- and thus the final feature count is
% 276.
%
Our classifiers are:
%
\begin{description}
\item[\linear] A logistic regression trained with a learning rate
  $\eta = 0.001$, an $L_2$ regularization rate $\lambda = 0.001$, and a
  mini-batch size of 200.
\item[\dectree] A decision tree trained with the CART algorithm
  \citep{Breiman1984-qy} and an impurity threshold of $10^{-7}$ (used to
  avoid overfitting via early stopping).
\item[\forest] A random forest \citep{Breiman2001-wo} of 30
  estimators, trained with an impurity threshold of $10^{-7}$.
\item[\hiddenT and \hiddenFH] Two multi-layer perceptron neural
  networks, both trained with $\eta = 0.001$, $\lambda = 0.001$, and a
  mini-batch size of 200. The first MLP contains a single hidden layer
  of 10 neurons, and the second contains a hidden layer of 500
  neurons. This allows us to investigate how well the MLP can
  \emph{compress} its model (cf.~\cite{FIXME}). The neurons use
  rectified linear units (ReLU) as their activation function, a common
  practice in modern neural networks.
\end{description}
%
All classifiers were trained for 20 epochs on one dataset
--- \ie they were shown each program 20 times ---
before being evaluated on the other.
%
The logistic regression and MLPs were trained with the \textsc{Adam}
optimizer \citep{Kingma2014-ng}, a variant of stochastic gradient
descent that has been found to converge faster.

@@

\paragraph{Results}
\autoref{fig:accuracy-results} shows the results of our experiment.
%
Localizing the type errors in our benchmarks amounted, on average, to
selecting one of 3 correct locations out of a slice of 10.
%
Our baseline of selecting at random achieves 30\% Top-1
accuracy (58\% Top-3), while \ocaml achieves a Top-1 accuracy of 45\%.
%
Interestingly, one only needs two \emph{random} guesses to outperform
\ocaml, with 47\% accuracy.
%
\sherrloc outperforms both baselines with 56\% Top-1 accuracy (84--86\% Top
3), while \mycroft actually underperforms \ocaml with 38--41\% Top-1
accuracy.
%
Finally, we find that \emph{all} of our classifiers outperform \sherrloc,
ranging from 58--62\% Top-1 accuracy (86--88\% Top-3) for the \linear
classifier to 71--74\% Top-1 accuracy (91\% Top-3) for the \hiddenFH.

### 2017-04-09 paper/oopsla17-submission/evaluation-utility.tex
misc

\ExprSize is the weakest feature, improving \linear Top-1
accuracy by less than 1\% and \hiddenFH by only 3\%.
%
In contrast, the contextual syntactic features improve \linear Top-1
accuracy by 5\% (\resp 14\%), and the typing features improve
Top-1 accuracy by 7\% (\resp 16\%).
%
Furthermore, while \ExprSize does provide some benefit when it is the
only additional feature, it does not appear to provide any real increase
in accuracy when added alongside the contextual or typing features.
\ES{FIXME: Indicate that this is expected because of feature overlap: the
contextual ``child'' features partially encode subtree size.}

>>>>

\ExprSize is the weakest feature, improving \linear Top-1
accuracy by less than 1\% and \hiddenFH by only 3\%.
%
In contrast, the contextual syntactic features improve \linear Top-1
accuracy by 5\% (\resp 14\%), and the typing features improve
Top-1 accuracy by 7\% (\resp 16\%).
%
Furthermore, while \ExprSize does provide some benefit when it is the
only additional feature, it does not appear to provide any real increase
in accuracy when added alongside the contextual or typing features.
%
This is likely explained by \emph{feature overlap}, \ie the contextual
features of ``child'' expressions additionally provide some information
about the size of the subtree.
